Type-safe client-server communication for web applications

### 2014-02-28 paper.tex
Don't Overuse Capitals In The Title
Update keywords.
Add explanation as to why there's a bunch of Haste stuff here.

\title{Type-Safe Client-Server Communication in Web Applications}
\subtitle{Subtitle Text, if any}

@@

% general terms are not compulsory anymore, 
% you may leave them out
%\terms
%term1, term2
%
\keywords
web

@@

>>>>

\title{Type-safe client-server communication for web applications}
\subtitle{Subtitle Text, if any}

@@

% general terms are not compulsory anymore, 
% you may leave them out
%\terms
%term1, term2
%
\keywords
web applications; distributed systems; network communication

@@

This paper also describes the Haste Haskell compiler in some detail, as it is a
crucial part of our implementation.
